---
title: "text_lab"
author: "Josephine Johannes"
date: "10/20/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Congratulations you've successfully transferred from being a NBA 'quant' scout to a consultant specializing in US national sentiment! You've been hired by a non-profit in secret to track the level of support nationally and regionally for the Climate Change issues. The goal is to get a general idea of patterns associated with articles being written on the broad topic of Climate Change (you can also choose to select a sub-topic). In doing so your data science team has decided to explore periodicals from around the country in a effort to track the relative positive or negative sentiment and word frequencies. Luckily you have access to a world class library search engine call LexusNexus (NexusUni) that provides access to newspapers from around the country dating back decades. You'll first need to decided what words you want to track and what time might be interesting to begin your search. 

Your main goal (and the goal of all practicing data scientists!) is to translate this information into action. What patterns do you see, why do you believe this to be the case? What additional information might you want? Be as specific as possible, but keep in mind this is an initial exploratory effort...more analysis might be needed...but the result can and should advise the next steps you present to the firm. 

## What we're tracking 
Essentially, we used the phrase "Climate Change" for various regions to track sentiment in 2021.


#### Loading Essential Libraries 
```{r, echo=FALSE}
library(tidyverse)
library(tidytext)
library(ggwordcloud) 
library(textdata)
library(rtf)
```

## MidAtlantic Region 
The text document was downloaded from the Lexis Nexis database. 30 of the most recent newspapers in Pennsylvania, written by the Pittsburgh Post-Gazette, were compiled as one RTF file and converted into an text file. 

#### Load in Mid Atlantic Region File
```{r} 
# import data from compiled newspaper reading
mid_atl <- read_lines("MidAtlanticRegion.txt")
# make mid_atl into a tibble data structure
mid_atl <- tibble(mid_atl)
```

#### Word Frequencies
1. The first step in the process is finding the frequency of words per region by tokenizing the document.
```{r}
#change the data frame variables in mid_atl$mid_atl character types
mid_atl$mid_atl <- as.character(mid_atl$mid_atl)

# tokenize mid_atl by word, take out common words like a, and count the number of words 
mid_atl <- mid_atl %>% 
  unnest_tokens(word, mid_atl) %>%
  anti_join(stop_words) %>% count(word, sort=TRUE)
```

#### Sentiment Analysis 
2. Using the word frequency from step 1, we use lexicons that help to classify the words in the documents using sentiment. 
```{r}
mid_atl_sentiment_affin <- mid_atl %>% inner_join(get_sentiments('afinn'))

mid_atl_sentiment_nrc <- mid_atl %>% inner_join(get_sentiments('nrc'))

mid_atl_sentiment_bing <- mid_atl %>% inner_join(get_sentiments('bing'))

table(mid_atl_sentiment_bing$sentiment)

table(mid_atl_sentiment_nrc$sentiment)
```

From the nrc lexicon, it would seem that most articles have a positive sentiment on climate change and the next highest sentiment would be negative. 

#### Plot Sentiment 
```{r}
ggplot(data = mid_atl_sentiment_affin, aes(x=value))+geom_histogram()+ggtitle("Mid Atlantic Region Sentiment Range")+theme_minimal()
```


From the histogram, it seems that there are more words that have a negative sentiment, compared to the amount of words with a positive sentiment. This could be related to how Pennsylvania had recently been hit by Hurricane Ida and is still in the process of recovering from the natural disaster. Governor Tim Wolf also announced the Pennsylvania Climate Action Plan 2021 which may have increased the amount of articles released recently. 

#### Another way to analyze Sentiment 
Here we use the ggplot package 
```{r}
set.seed(42)
ggplot(mid_atl[1:100,], aes(label = word, size = n))+geom_text_wordcloud()+theme_minimal()

```


#### Results: 

There are frequent words in the documents that include science, emissions, global, energy, warming, natural, and university, excluding the words climate and change. I think it would be a good idea to look at different universities and see the overall support for climate change there as well as bigger urban areas. I would say that Pittsburgh is a big urban area that uses a lot of energy so there could be negative sentiment due to the energy consumption in the city. It seems like there has been a correlation with the science as evidence for climate change, so a more negative sentiment could also be seen in scholarly literature. 

## NorthEast Region 
The text document was downloaded from the Lexus Nexus database. 30 of the most recent newspapers written by the Bangor Daily News in Maine were compiled as one RTF file and converted into an text file. 


#### Load in NorthEast Region File
```{r} 
# import data from compiled newspaper reading
north <- read_lines("NorthEastRegion.txt")
# make north into a tibble data structure
north <- tibble(north)
```

#### Word Frequencies
1. The first step in the process is finding the frequency of words per region. 
```{r}
#change the data frame variables in north$north character types
north$north <- as.character(north$north)

north <- north %>% 
  unnest_tokens(word, north) %>%
  anti_join(stop_words) %>% count(word, sort=TRUE)
```

#### Sentiment Analysis 
```{r}
north_sentiment_affin <- north %>% inner_join(get_sentiments('afinn'))
north_sentiment_nrc <- north %>% inner_join(get_sentiments('nrc'))
north_sentiment_bing <- north %>% inner_join(get_sentiments('bing'))

table(north_sentiment_bing$sentiment)

table(north_sentiment_nrc$sentiment)
```


From the nrc sentiment, it seems that the emotion most felt in the articles is positive and then the second highest emotion would be negative emotions.


#### Plot Sentiment 
```{r}
ggplot(data = north_sentiment_affin, aes(x=value))+geom_histogram()+ggtitle("Northeast Region Sentiment Range")+theme_minimal()
```


From the graph, it seems like there are more words that have a negative sentiment compared to those with a positive sentiment. 

#### Another way to analyze Sentiment 
Here we use the ggplot package 
```{r}
set.seed(42)
ggplot(north[1:100,], aes(label = word, size = n))+geom_text_wordcloud()+theme_minimal()

```


#### Results 
Excluding the words "climate", "change", and "maine", it seems like the most frequent words that come up are carbon, warming, bangor, maple, and energy. I think it would be interesting to look at the carbon industry in Maine and see how the environment has been impacted through that industry. If there are carbon plants, this could lead to negative sentiment for climate change because it would decrease profitability for the plants. It's also interesting how maple showed up in the climate change articles because maple is actually important for Maine's economy as the maple syrup industry is one of it's biggest industries. There have been some studies that have shown how climate change negatively impacts the maple syrup industry, so without context, it would have been unnerving to see maple in a climate change word cloud. 


#### Conducting the tf-idf 
```{r}
mid_atl_raw <- as.tibble(read_lines("MidAtlanticRegion.txt"))
north_raw <- as.tibble(read_lines("NorthEastRegion.txt"))
data_prep <- function(x,y,z){
  i <- as_tibble(t(x))#transposing the data set
  ii <- unite(i,"text",y:z,remove = TRUE,sep = "")
}
mid_atl_bag <- data_prep(mid_atl_raw,'V1','V2088')
north_bag<- data_prep(north_raw,'V1','V1979')
region <- c("MidAtlantic Region","NorthEast Region")
tf_idf_text <- tibble(region,text=t(tibble(mid_atl_bag,north_bag,.name_repair = "universal")))
View(tf_idf_text)
word_count <- tf_idf_text %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(region, word, sort = TRUE)
View(word_count)
total_words <- word_count %>% 
  group_by(region) %>% 
  summarize(total = sum(n))
region_words <- inner_join(word_count, total_words)
region_words <- region_words %>%
  bind_tf_idf(word, region, n)
View(region_words)
```


From the tf-idf, we were able to see some of the more popular words across the MidAtlantic region and the NorthEast region. Excluding the words "climate" and "change", the most important words seemed to be Pittsburgh and Bangor. This makes sense as it's the names of the newspapers but could be filtered out. The next most important words were syrup and mayewski. Through research, I found that Mayewski is the director and professor of the Climate Change Institute at the University of Maine. I also found in some other articles that climate change is negatively impacting Maine's maple syrup industry which is an essential factor in Maine's economy, leading to the negative sentiment behind climate change.


### Recommendations 
To look more specifically at the various stakeholders involved in climate change for the overall regions, I would recommend looking into universities as well as their faculty and carbon plants for each region respectively. Although there might be a higher negative sentiment in those areas, it would be interesting to find out the context as to why there is such a negative sentiment. In more recent news, I think more studies have been conducted on climate change and how the world is losing the necessary sources to survive at a faster pace than calculated, which leads into emotions like fear and anger. Overall, it would be important to look at the different stakeholders. 
